---
title: "Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `DART` package accompanies the paper "DART: distance assisted recursive testing" (arXiv link: https://arxiv.org/abs/2103.11085). It is designed to conduct powerful multiple testing under the assumption that hypotheses lies in a metric space with know distance matrix, which partially inform the co-null/co-alternative status.

```{r setup}
library(DART)
```
Here, we show how to apply `DART` based the P-values and distance matrix.
\par
The sample data we used to analysis is from a microbiome study with $n=456$ samples and $m=857$  amplicon sequence variants (ASVs). Each ASV can be viewed as a testing unit and links to a hypothesis. Based on preprocessing process, we can get the distance matrix among the $m=857$ ASVs (`Dist0`) and a vector of p-values links to each hypotheses (`pvals`). Please refer to the paper for the in depth information (e.g. data preprocess, hypotheses set up, tuning parameter selection, etc.) about the data analysis.


```{r}
# Setting up tuning parameters. Please refer to the paper for detailed tuning parameter selection procedure.
n <- 456
m <- 857
grids <- c(16,16)/sqrt(n*log(m)*log(log(m)))
Mgroup <- floor(log(m/35,3))

# Stage 1: build aggregation tree
Atree <- A.tree.mult(grids=grids,Mgroup = Mgroup, Dist0 = Dist0)
# Stage 2: Embed multiple testing in the aggregation tree
Test.result <- test.mult(alpha=0.05,Llist=Atree$Llist,Dist0=Dist0,T1=t(qnorm(pvals,lower.tail=FALSE)))

Test.result

```

